Irt plot extra

### 2022-02-22 manuscript.Rmd
gtPlots updated

as_tibble(desc_table) -> desc_tibble 
as_kable_extra(desc_table, format = "latex",booktabs = T) -> desc_kable #save it as a knitr::kable

@@

Table \@ref(tab:demotab) summarizes the survey participants' demographic characteristics. Only participants completing the full LEBA questionnaire were included, thus there are no missing values in the item analyses. (XX??) participants were excluded from analysis due to not passing at least one of the "attention check" items. For EFA, a sample of 250-300 is recommended [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013]. To assess sampling adequacy for CFA, we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006], where ten participants per item is required to earn trustworthiness of the result. Both our EFA and CFA sample size exceeded these requirements.
We collected data from `r nrow(num.countries)` countries (`r nrow(numUTC)` time zones).Participants reported a diverse range of geographic location
Participants indicated filling out the online survey from a diverse range of geographic locations. Figure \@ref(fig:partmap) depicts the top ten countries with highest participation in our survey. For a complete list of geographic locations, see Suppl. Table \@ref(tab:tztable).

```{r partmap, fig.cap="Top ten countries with highest responses in our survey", out.height= '100%', out.width= '100%'}
knitr::include_graphics('Manuscript.figures/distribution.png', dpi = 300 )
```

```{r rafael2, eval=FALSE, include=FALSE}
# - `r tz_tibble[2,1]`:     `r tz_tibble[2,2]`
# - `r tz_tibble[3,1]`:     `r tz_tibble[3,2]`
# - `r tz_tibble[4,1]`:     `r tz_tibble[4,2]`
# - `r tz_tibble[5,1]`:     `r tz_tibble[5,2]`
# - `r tz_tibble[6,1]`:     `r tz_tibble[6,2]`
# - `r tz_tibble[7,1]`:     `r tz_tibble[7,2]`
# - `r tz_tibble[8,1]`:     `r tz_tibble[8,2]`
# - `r tz_tibble[9,1]`:     `r tz_tibble[9,2]`
# - `r tz_tibble[10,1]`:    `r tz_tibble[10,2]`
# - `r tz_tibble[11,1]`:    `r tz_tibble[11,2]`
```

@@

efa.gt %>% 
gt() %>% 
# histogram and density plots
  gtExtras::gt_sparkline(
    hist_data,
    type = "histogram",
    line_color = "black", 
    fill_color = "#00A08799",
    bw = 1,
    same_limit = TRUE)%>%
  gtExtras::gt_sparkline(
    dens_data,
    type = "density",
    line_color = "black", 
    fill_color = "#E64B3599",
    bw = 0.75,
    same_limit = TRUE
  )%>%
# format decimals
  fmt_number(columns = mean:sd, decimals = 1) %>%
# header
  tab_header(
    title = md("**LEBA**"),
    subtitle = md("Summary Descriptives EFA Sample (n =428)")
  ) %>% 
  tab_footnote(
    footnote = md("**Histogram**"),
    locations = cells_column_labels(columns = hist_data)
  ) %>%
  tab_footnote(
    footnote = md("**Density**"),
    locations = cells_column_labels(columns = dens_data)
  ) %>% 
#create groups of columns
tab_spanner(
  label = "Items",
  columns = Items
) %>%
  tab_spanner(
    label = "Summary Statistics",
    columns = nr:sd
  ) %>%
  tab_spanner(
    label = "Graphics",
    columns = hist_data:dens_data
  ) %>% 
  tab_spanner(
    label = "Response Pattern",
    columns = Never:Always
  ) %>%
# change column names to appear in the table
cols_label(
  Items = ("LEBA  Items"),
  nr = ("n"),
  mean = ("Mean"),
  med = ("Median "),
  sd = (("SD")),
  hist_data = "Histogram",
  dens_data = "Density"
) %>%
# set alignment as per wish
  cols_align(
    align = "center",
    columns = everything()
  ) %>%
  opt_align_table_header(align = "left") %>%
# add coloured dots and lines on the first column
  gt_plt_dot(
    mean,
    Items,
    palette = "ggthemes::fivethirtyeight") %>% 
  tab_row_group(
      label = md("**F5:Using light in the morning and during daytime**"),
      rows = c(1,3,12,13,24,25) 
        ) %>% 
  tab_row_group(
      label = md("**F4:Using light before bedtime**"),
      rows = c(16,17,18,20,21) 
        ) %>% 
  tab_row_group(
      label = md("**F3:Using phone and smart-watch in bed**"),
      rows = c(2,14,15,22,23) 
        ) %>% 
  tab_row_group(
      label = md("**F2:Spending time outdoors**"),
      rows = c(4,5,6,7,8,9) 
        ) %>% 
  tab_row_group(
      label = md("**F1:Wearing blue light filters**"),
      rows = c(10,11,19) 
        ) %>% gtsave("Manuscript.figures/efagt.png",vwidth = 7000)

@@

cfa.gt %>% 
gt() %>% 
# histogram and density plots
  gtExtras::gt_sparkline(
    hist_data,
    type = "histogram",
    line_color = "black", 
    fill_color = "#00A08799",
    bw = 1,
    same_limit = TRUE)%>%
  gtExtras::gt_sparkline(
    dens_data,
    type = "density",
    line_color = "black", 
    fill_color = "#E64B3599",
    bw = 0.75,
    same_limit = TRUE
  )%>%
# format decimals
  fmt_number(columns = mean:sd, decimals = 1) %>%
# header
  tab_header(
    title = md("**LEBA**"),
    subtitle = md("Summary Descriptives CFA Sample (Nn=262)")
  ) %>% 
  tab_footnote(
    footnote = md("**Histogram**"),
    locations = cells_column_labels(columns = hist_data)
  ) %>%
  tab_footnote(
    footnote = md("**Density**"),
    locations = cells_column_labels(columns = dens_data)
  ) %>% 
#create groups of columns
tab_spanner(
  label = "Items",
  columns = Items
) %>%
  tab_spanner(
    label = "Summary Statistics",
    columns = nr:sd
  ) %>%
  tab_spanner(
    label = "Graphics",
    columns = hist_data:dens_data
  ) %>% 
  tab_spanner(
    label = "Response Pattern",
    columns = Never:Always
  ) %>%
# change column names to appear in the table
cols_label(
  Items = ("LEBA Items"),
  nr = ("n"),
  mean = ("Mean"),
  med = ("Median "),
  sd = (("SD")),
  hist_data = "Histogram",
  dens_data = "Density"
) %>%
# set alignment as per wish
  cols_align(
    align = "center",
    columns = everything()
  ) %>%
  opt_align_table_header(align = "left") %>%
# add coloured dots and lines on the first column
  gt_plt_dot(
    mean,
    Items,
    palette = "ggthemes::fivethirtyeight") %>% 
  tab_row_group(
      label = md("**F5:Using light in the morning and during daytime**"),
      rows = c(1,3,12,13,22,23) 
        ) %>% 
  tab_row_group(
      label = md("**F4:Using light before bedtime**"),
      rows = c(15,16,17,19) 
        ) %>% 
  tab_row_group(
      label = md("**F3:Using phone and smart-watch in bed**"),
      rows = c(2,13,14,20,21) 
        ) %>% 
  tab_row_group(
      label = md("**F2:Spending time outdoors**"),
      rows = c(4,5,6,7,8,9) 
        ) %>% 
  tab_row_group(
      label = md("**F1:Wearing blue light filters**"),
      rows = c(10,11,18) 
        ) %>% 
  gtsave("Manuscript.figures/cfagt.png",vwidth = 7000)

@@

```{r Testinfo, fig.cap="Test information curves (a) wearing blue light filters (b) spending time outdoors (c) using phone and smartwatchin bed (d) using light before bedtime (e) using light in the morning andduring daytime", warning=FALSE}

>>>>

as_tibble(desc_table) -> desc_tibble 
as_kable_extra(desc_table, format = "latex",booktabs = T) %>% 
  kable(col.names=c("Variable", "Overall, n=690$^{1}$","EFA Sample, n=428$^{1}$", "CFA sample, n=262$^{1}$", "p", "q$^{2}$"), escape = FALSE)-> desc_kable #save it as a knitr::kable

@@

Table \@ref(tab:demotab) summarizes the survey participants' demographic characteristics. Only participants completing the full LEBA questionnaire were included, thus there are no missing values in the item analyses. (XX??) participants were excluded from analysis due to not passing at least one of the "attention check" items. For EFA, a sample of 250-300 is recommended [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013]. To assess sampling adequacy for CFA, we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006], where ten participants per item is required to earn trustworthiness of the result. Both our EFA and CFA sample size exceeded these requirements.
We collected data from `r nrow(num.countries)` countries (`r nrow(numUTC)` time zones).Participants reported a diverse range of geographic location
Participants indicated filling out the online survey from a diverse range of geographic locations. For a complete list of geographic locations, see Suppl. Table \@ref(tab:tztable).

```{r partmap, eval=FALSE, fig.cap="Top ten countries with highest responses in our survey", include=FALSE, out.height='100%', out.width=}
knitr::include_graphics('Manuscript.figures/distribution.png', dpi = 300 )
```

```{r rafael2, eval=FALSE, include=FALSE}
# Figure \@ref(fig:partmap) depicts the top ten countries with highest participation in our survey.
# - `r tz_tibble[2,1]`:     `r tz_tibble[2,2]`
# - `r tz_tibble[3,1]`:     `r tz_tibble[3,2]`
# - `r tz_tibble[4,1]`:     `r tz_tibble[4,2]`
# - `r tz_tibble[5,1]`:     `r tz_tibble[5,2]`
# - `r tz_tibble[6,1]`:     `r tz_tibble[6,2]`
# - `r tz_tibble[7,1]`:     `r tz_tibble[7,2]`
# - `r tz_tibble[8,1]`:     `r tz_tibble[8,2]`
# - `r tz_tibble[9,1]`:     `r tz_tibble[9,2]`
# - `r tz_tibble[10,1]`:    `r tz_tibble[10,2]`
# - `r tz_tibble[11,1]`:    `r tz_tibble[11,2]`
```

@@

efa.gt %>% 
gt() %>% 
# histogram and density plots
  gtExtras::gt_sparkline(
    hist_data,
    type = "histogram",
    line_color = "black", 
    fill_color = "#00A08799",
    bw = 1,
    same_limit = TRUE)%>%
  gtExtras::gt_sparkline(
    dens_data,
    type = "density",
    line_color = "black", 
    fill_color = "#E64B3599",
    bw = 0.75,
    same_limit = TRUE
  )%>%
# format decimals
  fmt_number(columns = mean:sd, decimals = 1) %>%
# header
  tab_header(
    title = md("**Light Exposure Behavior Assessment**"),
    subtitle = md("Summary Descriptives EFA Sample (n =428)")
  ) %>% 
  # tab_footnote(
  #   footnote = md("**Histogram**"),
  #   locations = cells_column_labels(columns = hist_data)
  # ) %>%
  # tab_footnote(
  #   footnote = md("**Density**"),
  #   locations = cells_column_labels(columns = dens_data)
  # ) %>% 
#create groups of columns
tab_spanner(
  label = "Items",
  columns = Items
) %>%
  tab_spanner(
    label = "Summary Statistics",
    columns = nr:sd
  ) %>%
  tab_spanner(
    label = "Graphics",
    columns = hist_data:dens_data
  ) %>% 
  tab_spanner(
    label = "Response Pattern",
    columns = Never:Always
  ) %>%
# change column names to appear in the table
cols_label(
  Items = (""),
  nr = ("n"),
  mean = ("Mean"),
  med = ("Median "),
  sd = (("SD")),
  hist_data = "Histogram",
  dens_data = "Density"
) %>%
# set alignment as per wish
  cols_align(
    align = "center",
    columns = everything()
  ) %>%
  opt_align_table_header(align = "left") %>%
# add coloured dots and lines on the first column
  gt_plt_dot(
    mean,
    Items,
    palette = "ggthemes::fivethirtyeight") %>% 
  tab_row_group(
      label = md("**F5: Using light in the morning and during daytime**"),
      rows = c(1,3,12,13,24,25) 
        ) %>% 
  tab_row_group(
      label = md("**F4: Using light before bedtime**"),
      rows = c(16,17,18,20,21) 
        ) %>% 
  tab_row_group(
      label = md("**F3: Using phone and smart-watch in bed**"),
      rows = c(2,14,15,22,23) 
        ) %>% 
  tab_row_group(
      label = md("**F2: Spending time outdoors**"),
      rows = c(4,5,6,7,8,9) 
        ) %>% 
  tab_row_group(
      label = md("**F1: Wearing blue light filters**"),
      rows = c(10,11,19) 
        ) %>% gtsave("Manuscript.figures/efagt.png",vwidth = 7000)

@@

cfa.gt %>% 
gt() %>% 
# histogram and density plots
  gtExtras::gt_sparkline(
    hist_data,
    type = "histogram",
    line_color = "black", 
    fill_color = "#00A08799",
    bw = 1,
    same_limit = TRUE)%>%
  gtExtras::gt_sparkline(
    dens_data,
    type = "density",
    line_color = "black", 
    fill_color = "#E64B3599",
    bw = 0.75,
    same_limit = TRUE
  )%>%
# format decimals
  fmt_number(columns = mean:sd, decimals = 1) %>%
# header
  tab_header(
    title = md("**Light Exposure Behavior Assessment**"),
    subtitle = md("Summary Descriptives CFA Sample (n=262)")
  ) %>% 
  # tab_footnote(
  #   footnote = md("**Histogram**"),
  #   locations = cells_column_labels(columns = hist_data)
  # ) %>%
  # tab_footnote(
  #   footnote = md("**Density**"),
  #   locations = cells_column_labels(columns = dens_data)
  # ) %>% 
#create groups of columns
tab_spanner(
  label = "Items",
  columns = Items
) %>%
  tab_spanner(
    label = "Summary Statistics",
    columns = nr:sd
  ) %>%
  tab_spanner(
    label = "Graphics",
    columns = hist_data:dens_data
  ) %>% 
  tab_spanner(
    label = "Response Pattern",
    columns = Never:Always
  ) %>%
# change column names to appear in the table
cols_label(
  Items = (""),
  nr = ("n"),
  mean = ("Mean"),
  med = ("Median "),
  sd = (("SD")),
  hist_data = "Histogram",
  dens_data = "Density"
) %>%
# set alignment as per wish
  cols_align(
    align = "center",
    columns = everything()
  ) %>%
  opt_align_table_header(align = "left") %>%
# add coloured dots and lines on the first column
  gt_plt_dot(
    mean,
    Items,
    palette = "ggthemes::fivethirtyeight") %>% 
  tab_row_group(
      label = md("**F5: Using light in the morning and during daytime**"),
      rows = c(1,3,12,13,22,23) 
        ) %>% 
  tab_row_group(
      label = md("**F4: Using light before bedtime**"),
      rows = c(15,16,17,19) 
        ) %>% 
  tab_row_group(
      label = md("**F3: Using phone and smart-watch in bed**"),
      rows = c(2,13,14,20,21) 
        ) %>% 
  tab_row_group(
      label = md("**F2: Spending time outdoors**"),
      rows = c(4,5,6,7,8,9) 
        ) %>% 
  tab_row_group(
      label = md("**F1: Wearing blue light filters**"),
      rows = c(10,11,18) 
        ) %>% 
  gtsave("Manuscript.figures/cfagt.png",vwidth = 7000)

@@

```{r Testinfo, fig.cap="Test information curves for the five factors of LEBA: (a) wearing blue light filters (b) spending time outdoors (c) using phone and smartwatchin bed (d) using light before bedtime (e) using light in the morning andduring daytime. Along x-axis we plotted the underlying latent trait continumm for each factor. Along y-axis we plotted how much information a particular factor is caring across its latent trait continuum", warning=FALSE}
